Block bootstrap consistency\\under weak assumptions

### 2017-01-10 subs/ETr4/reply_3.tex
[#29/typo] Add response to referee
[#31/grammar] Add response to referee
[#33/lem1] Add reply to referee

@@

@@

@@

@@

@@

\item \emph{Since these arguments are nonnegative (they're
    probabilities), what is the purpose of enclosing them in absolute
    value bars?} (Page 15, line --5) 
\end{enumerate}

>>>>

It should be $\pi$. Thanks for catching this error.

@@

Fixed, thanks.

@@

  Yes, for $\Em(\cdot)$. The other terms look correct, though.

@@

  This is correct. I have also added your clarification to the paper
  (if you don't mind, of course) to help other readers see these
  essential differences.

@@

  Ok. My primary motivation in writing that statement was to avoid
  appearing to take credit for a standard argument in this
  literature. (I was asked to include these steps explicitly by an
  earlier referee.)  I have added a reference to van der Vaart's
  (2000) textbook instead, since I've been unable to track down a
  specific citation for Poly\'a.

@@

  This first result has been cleaned up a little bit.

\item \emph{Since these arguments are nonnegative (they're
    probabilities), what is the purpose of enclosing them in absolute
    value bars?} (Page 15, line --5)

  They are enclosed in absolute value bars to make the connection to the
  $L_{1}$-norm explicit. I've removed the absolute value sign from the first
  probability to reduce confusion.

\end{enumerate}
